BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2015-03-13 Paper/D5.5/D5.5.tex
Added more conclusion.

In this report we presented the BOAST infrastructure as well as its
application to two use cases from the Mont-Blanc project. Results are
encouraging as BOAST proved to be a powerful and flexible tool.

>>>>

In this report we presented the BOAST infrastructure as well as its
application to three use cases from the Mont-Blanc project. Results are
encouraging as BOAST proved to be a powerful and flexible tool that allowed
gains in performance and performance portability.

Future development will focus on three goals. Interfacing with binary analysis
tools like MAQAO~\cite{djoudi2005exploring} in order to build a feedback loop to
guide optimization. Interfacing with search space modellers/pruners in order to
optimize the search of the optimal version of a kernel. Continue working on
vector code. For instance producing a collection of small to medium useful
vector patterns (transposition for instance) in BOAST could really help develop
vectorized version of our algorithm.
